Optimizing a PoS Tag Set for Dependency Parsing

### 2016-05-05 submission.tex
Added results to each PoS. Unminor changes to section 5 and 6, tables and all

Our approach is somewhat semi-automatic in that we employ a "hybrid"
combination of manual annotation and automatic labeling in our experiments. Our
initial tags are gold standard, and using linguistic insight coupled with
computational considerations, we introduce new features or feature combination
to the tag set. These tags are run through a pipeline with automatically
assigned tags in both training and testing, where the most promising
modifications are used "further". Hence, the tag set modifications are not
deterministic, nor do we try all possible combination; we only experiment with
linguistically motivated distinctions. We are in reality altering the gold
standard tags by the addition of more linguistic information.

@@

\section{Tag Set Optimization}
\label{sec:optimization}
By introducing more fine-grained linguistically motivated distinctions in a tag
set, we increase the linguistic information represented in the tags, which may
assist the parser in recognizing and generalizing syntactic patterns. However,
the addition of more linguistic information to the tags and thus a more
fine-grained tag set will most likely lead to a drop in tagger accuracy due to
the increase in complexity. The best tagging does not necessarily lead to the
best parse, hence it is interesting to investigate how linguistically informed
tag set modifications may affect the interplay between tagging and parsing.
%As
%we want to investigate how we can improve the linguistic quality of a tag set,
%we will
%only consider tag set modifications we deem linguistically sensible.
%we will not introduce tag set modifications which are not linguistically
%motivated. We will only consider distinctions we deem linguistically sensible.

@@

\begin{table}
    \centering
    \smaller[0.5]
    \begin{tabular}{@{}lllll@{}}
        \toprule
        \textbf{Tag set} & \textbf{MFT} & \textbf{Accuracy} &
        \textbf{LAS} & \textbf{UAS} \\
        \midrule
        Original & \textbf{94.14\%} & \textbf{97.47\%} & 87.01\% & 90.19\% \\
        Full & 85.15\% & 93.48\% & \textbf{87.15\%} & \textbf{90.39\%} \\
        \bottomrule
    \end{tabular}
    \caption{Results of tagging and parsing with the two initial tag sets.}
    \label{inittagseteval}
\end{table}

@@

The morphological properties of the various parts-of-speech are reflected in
the morphological features associated with the respective PoS tags. For
instance, as nouns in Norwegian can take on gender, definiteness and number,
additionally marked with genitive case, the treebank operates with features for
gender, definiteness, number and case.
%with "accompanying" values
In addition to morphological properties such as definiteness, tense and number,
all classes except for verbs can be distinguished "on" type, e.g., common nouns
and proper nouns, while pronouns can be reflexive, reciprocal, personal or
interrogative.

@@

\begin{table}
    \centering
    \smaller[1]
    \begin{tabular}{@{}llll@{}}
        \toprule
        \textbf{Feature(s)} & \textbf{Acc} & \textbf{LAS} & \textbf{UAS}
        \\
        \midrule
        --- & 97.47\% & 87.01\% & 90.19\% \\
        Case & \textbf{97.48\%} & 87.63\% & 90.72\% \\
        Definiteness & 97.00\% & 88.27\% & 91.42\% \\
        Gender & 96.09\% & 87.21\% & 90.36\% \\
        Number & 96.37\% & 87.97\% & 91.00\% \\
        Type & 96.92\% & 88.07\% & 91.11\% \\
        Case \& definiteness & 97.03\% & 88.39\% & 91.44\% \\
        Type \& case & 96.92\% & 88.46\% & 91.51\% \\
        Type \& definiteness & 96.99\% & 88.44\% & 91.48\% \\
        Type \& number & 96.37\% & 87.95\% & 90.95\% \\
        Type, case \& definiteness & 97.05\% & \textbf{88.81\%} &
        \textbf{91.73\%} \\
        %Type, definiteness \& number & 96.46\% & 88.06\% & 91.12\% \\
        \bottomrule
    \end{tabular}
    \caption{Results of experiments with modified PoS tags for nouns.}
    \label{substresults}
\end{table}

@@

Table \ref{adjresults}

All features except for number led to increases in parser accuracy scores.
Degree being the most promising with a reported LAS of 87.29\%, while
distinguishing adjectives on definiteness yield an LAS of 87.14\% and gender
leads to LAS of 87.10\%.

Combining the most promising features, we found that none of the combinations
surpass the LAS with the distinction of degree alone. Definiteness and degree
with an LAS of 87.23\% and definiteness and number with an LAS of 87.27\% and
UAS identical to that of degree alone.

@@

\begin{table}
    \centering
    \smaller[0.5]
    \begin{tabular}{@{}llll@{}}
        \toprule
        \textbf{Feature(s)} & \textbf{Acc} & \textbf{LAS} & \textbf{UAS}
        \\
        \midrule
        --- & \textbf{97.47\%} & 87.01\% & 90.19\% \\
        Definiteness & 96.84\% & 87.14\% & 90.29\% \\
        Degree & 97.41\% & \textbf{87.29\%} & \textbf{90.44\%} \\
        Gender & 96.89\% & 87.10\% & 90.25\% \\
        Number & 96.71\% & 86.99\% & 90.10\% \\
        Type & 97.40\% & 87.11\% & 90.25\% \\
        Definiteness \& degree & 96.81\% & 87.23\% & 90.39\% \\
        Definiteness \& gender & 96.31\% & 87.18\% & 90.39\% \\
        Definiteness \& number & 96.78\% & 87.27\% & \textbf{90.44\%} \\
        Degree \& gender & 96.87\% & 87.00\% & 90.16\% \\
        Degree \& number & 96.76\% & 87.13\% & 90.26\% \\
        %Definiteness, degree \& number & 96.81\% & 87.14\% & 90.30\% \\
        \bottomrule
    \end{tabular}
    \caption{Results of experiments with modified PoS tags for adjectives.}
    \label{adjresults}
\end{table}

@@

For a number of reasons, we do not report results from combinations of features
for determiners, as the features could not be combined in any meaningful way.
For instance, determiners in plural never have marked definiteness, hence this
combination would only apply to determiners in singular and roughly correspond
to the distinction on definiteness alone. Moreover, determiners in plural are
not distinguished in terms of gender (thus ruling out the combination of number
and gender), neither are definite determiners. Another aspect taken into
consideration is that the most promising distinction, definiteness, applies to
such a small number of tokens that more fine-grained distinctions would be
overly sparse.

@@

Gender, on the other hand, improved the parsing, but complicated the tagging,
as the various genders are often difficult to differentiate, especially so in
the case of masculine and feminine, which share many of the same determiners.
The number of a determiner, i.e., singular or plural, led to a small increase
in tagger accuracy and LAS, while marginally lower UAS, 90.18\%, 0.01
percentage points lower than that of the original tag set. The
introduction of definiteness to the determiners led to the best parsing
results, LAS of 87.30\% and UAS of 90.42\%, while also increasing the tagger
accuracy slightly. The increase in LAS and UAS is rather interesting, as there
are only 121 "determiner tokens" with marked definiteness in the development
data. As this accounts for a very small number of tokens, coupled with the
previously noted considerations, we did not consider further fine-grained
modifications with definiteness. This goes to show that tokens with overt
definiteness have noticeable impact on the syntactic parsing, and that
distinguishing on definiteness is very beneficial.

@@

The results in Table \ref{pronresults} show that number, person and type are
the most informative features for parsing, with LAS of 87.21\%, 87.22\% and
87.19\%, respectively. However, when combining number and person, we observe a
drop by more than 0.2 percentage points, indicating that these features do not
interact in any syntactically distinctive way. The most interesting observation
is that all experiments exceed the baseline tagger accuracy, the most improved
being the most fine-grained distinction, namely type, case and number combined,
obtaining a tagger accuracy of 97.52\%. This shows that the introduction of
more fine-grained distinctions for pronouns is beneficial and aids the PoS
tagger in disambiguating ambiguous words. While case alone yields an LAS of
87.08\%, we found that the combination of type and case, which is the most
successful experiment in terms of parser performance, yields the second highest
tagging accuracy of 97.51\%. The reason for this is that pronouns of different
type and personal pronouns of different case exhibit quite different properties
and appear in different constructions. Pronouns in nominative case (i.e.,
subjects) primarily occur before the main verb, while pronouns in accusative
case (i.e., objects) occur after the main verb, as Norwegian exhibits so-called
V2 word order, requiring that the finite verb of a declarative clause appears
in the second position, hence its name. The combination of type and number
comes in close to the performance of type and case, with LAS of 87.27\% and UAS
identical to that of type and case.

@@

\subsection{Optimized Tag Set}
The most successful tag set modifications and their results are seen in Table
\ref{respectiveresults}.

\begin{table*}
    \centering
    \smaller[0.5]
    \begin{tabular}{@{}llllll@{}}
        \toprule
        \textbf{Category} & \textbf{Feature(s)} & \textbf{MFT} &
        \textbf{Accuracy} & \textbf{LAS} & \textbf{UAS} \\
        \midrule
        \emph{Baseline} & --- & 94.14\% & 97.47\% & 87.01\% & 90.19\% \\
        Noun & Type, case \& definiteness & 89.61\% & 97.05\% & 88.81\% &
        91.73\% \\
        Verb & Finiteness & 93.72\% & 97.35\% & 87.30\% & 90.43\% \\
        Adjective & Degree & 94.13\% & 97.41\% & 87.29\% & 90.44\% \\
        Determiner & Definiteness & 94.13\% & 97.49\% & 87.30\% & 90.42\% \\
        Pronoun & Type \& case & 94.12\% & 97.51\% & 87.30\% & 90.41\% \\
        \bottomrule
    \end{tabular}
    \caption{Results of tagging and parsing with the most successful tag set
        modification for each category.}
    \label{respectiveresults}
\end{table*}

An overview of the tags comprising the final, optimized tag set can be seen in
Table \ref{optimizedtagset}.

\begin{table}
    \centering
    \smaller[0.5]
    \begin{tabular}{@{}ll@{}}
        \toprule
        \textbf{Tag} & \textbf{Description} \\
        \midrule
        \texttt{adj|komp} & Comparative adjective \\
        \texttt{adj|pos} & Positive adjective \\
        \texttt{adj|sup} & Superlative adjective \\
        \texttt{det|be} & Definite determiner \\
        \texttt{det|ub} & Indefinite determiner \\
        \texttt{pron|pers} & Personal pronoun \\
        \texttt{pron|pers|akk} & Personal pronoun, accusative \\
        \texttt{pron|pers|nom} & Personal pronoun, nominative \\
        \texttt{pron|refl} & Reflexive pronoun \\
        \texttt{pron|res} & Reciprocal pronoun \\
        \texttt{pron|sp} & Interrogative pronoun \\
        \texttt{subst|appell} & Common noun \\
        \texttt{subst|appell|be} & Common noun, definite \\
        \texttt{subst|appell|be|gen} & Common noun, definite, genitive \\
        \texttt{subst|appell|ub} & Common noun, indefinite \\
        \texttt{subst|appell|ub|gen} & Common noun, indefinite, genitive \\
        \texttt{subst|prop} & Proper noun \\
        \texttt{subst|prop|gen} & Proper noun, genitive \\
        \texttt{verb|fin} & Finite verb \\
        \texttt{verb|infin} & Nonfinite verb \\
        \bottomrule
    \end{tabular}
    \caption{Overview of the optimized tag set.}
    \label{optimizedtagset}
\end{table}

Results from parsing with the optimized tag are shown in Table
\ref{finalresults}, compared to the results obtained with the initial tag sets.

\begin{table*}
    \centering
    \smaller[0.5]
    \begin{tabular}{@{}llllll@{}}
        \toprule
        \textbf{Data Set} & \textbf{Tag Set} & \textbf{MFT} & \textbf{Accuracy}
        & \textbf{LAS} & \textbf{UAS} \\
        \midrule
        \multirow{2}{*}{Dev}
        & Original & \textbf{94.14\%} & \textbf{97.47\%} & 87.01\% & 90.19\% \\
        %Full & 85.15\% & 93.48\% & 87.15\% & 90.39\% \\
        & Optimized & 89.20\% & 96.85\% & \textbf{88.87\%} & \textbf{91.78\%} \\
        \midrule
        \multirow{2}{*}{Test}
        & Original & \textbf{94.22\%} & \textbf{97.38\%} & 86.64\% & 90.07\% \\
        %& Full & 84.27\% & 92.79\% & 87.03\% & 90.16\% \\
        & Optimized & 88.08\% & 96.35\% & \textbf{88.55\%} & \textbf{91.41\%} \\
        \bottomrule
    \end{tabular}
    \caption{Results of tagging and parsing with the optimized tag set,
        compared to the initial tag sets. Trained and tested using
        automatically assigned tags from TnT.}
    \label{finalresults}
\end{table*}

>>>>

Our approach is somewhat semi-automatic in that we employ a "hybrid"
combination of manual annotation and automatic labeling in our experiments. Our
initial tags are gold standard, and using linguistic insight coupled with
computational considerations, we introduce new gold standard distinctions to
the tag set. The data sets with these tags are run through a pipeline with
automatically assigned tags in both training and testing, where the most
promising modifications are used "further". Hence, the tag set modifications
are not deterministic, nor do we try all possible combination; we only
experiment with linguistically motivated distinctions. We are in reality
altering the gold standard tags by the addition of more linguistic information.

As we want to investigate how we can improve the linguistic quality of a tag
set, we will only consider tag set modifications we deem linguistically
sensible.

@@

\section{Tag Set Optimization}
\label{sec:optimization}
By introducing more fine-grained linguistically motivated distinctions in a tag
set, we increase the linguistic information represented in the tags, which may
assist the parser in recognizing and generalizing syntactic patterns. However,
the addition of more linguistic information to the tags and thus a more
fine-grained tag set will most likely lead to a drop in tagger accuracy due to
the increase in complexity. The best tagging does not necessarily lead to the
best parse, hence it is interesting to investigate how linguistically informed
tag set modifications may affect the interplay between tagging and parsing.
%as
%we want to investigate how we can improve the linguistic quality of a tag set,
%we will
%only consider tag set modifications we deem linguistically sensible.
%we will not introduce tag set modifications which are not linguistically
%motivated. we will only consider distinctions we deem linguistically sensible.

@@

\begin{table}
    \centering
    \smaller[0.5]
    \begin{tabular}{@{}llll@{}}
        \toprule
        \textbf{Tag Set} & \textbf{Acc} &
        \textbf{LAS} & \textbf{UAS} \\
        \midrule
        Original & \textbf{97.47\%} & 87.01\% & 90.19\% \\
        Full & 93.48\% & \textbf{87.15\%} & \textbf{90.39\%} \\
        \bottomrule
    \end{tabular}
    \caption{Results of tagging and parsing with the two initial tag sets.}
    \label{inittagseteval}
\end{table}

@@

The morphological properties of the various parts-of-speech are reflected in
the morphological features associated with the respective PoS tags. For
instance, as nouns in Norwegian can take on gender, definiteness and number,
additionally marked with genitive case, the treebank operates with features for
gender, definiteness, number and case.
%with "accompanying" values
In addition to morphological properties such as definiteness, tense and number,
all classes except for verbs have a \emph{type} feature that provides
information about the subtype, e.g., common nouns and proper nouns, while
pronouns can be reflexive, reciprocal, personal or interrogative.

@@

\begin{table}
    \centering
    \smaller[1]
    \begin{tabular}{@{}llll@{}}
        \toprule
        \textbf{Feature(s)} & \textbf{Acc} & \textbf{LAS} & \textbf{UAS}
        \\
        \midrule
        --- & 97.47\% & 87.01\% & 90.19\% \\
        Case & \textbf{97.48\%} & 87.63\% & 90.72\% \\
        Definiteness & 97.00\% & 88.27\% & 91.42\% \\
        Gender & 96.09\% & 87.21\% & 90.36\% \\
        Number & 96.37\% & 87.97\% & 91.00\% \\
        Type & 96.92\% & 88.07\% & 91.11\% \\
        Case \& definiteness & 97.03\% & 88.39\% & 91.44\% \\
        Type \& case & 96.92\% & 88.46\% & 91.51\% \\
        Type \& definiteness & 96.99\% & 88.44\% & 91.48\% \\
        %Type \& number & 96.37\% & 87.95\% & 90.95\% \\
        Type, case \& definiteness & 97.05\% & \textbf{88.81\%} &
        \textbf{91.73\%} \\
        %Type, definiteness \& number & 96.46\% & 88.06\% & 91.12\% \\
        \bottomrule
    \end{tabular}
    \caption{Results of experiments with modified PoS tags for nouns.}
    \label{substresults}
\end{table}

@@

In Table \ref{adjresults}, we report the results of modifying the \texttt{pron}
tag in NDT. All features except for number led to increases in parser accuracy
scores, the most successful of which is degree with a reported LAS of 87.29\%,
while distinguishing adjectives on definiteness yield an LAS of 87.14\% and
gender leads to LAS of 87.10\%.

%Combining the most promising features, we
%found that none of the combinations surpass the LAS with the distinction of
%degree alone. Definiteness and degree with an LAS of 87.23\% and definiteness
%and number with an LAS of 87.27\% and UAS identical to that of degree alone.

@@

\begin{table}
    \centering
    \smaller[0.5]
    \begin{tabular}{@{}llll@{}}
        \toprule
        \textbf{Feature(s)} & \textbf{Acc} & \textbf{LAS} & \textbf{UAS}
        \\
        \midrule
        --- & \textbf{97.47\%} & 87.01\% & 90.19\% \\
        Definiteness & 96.84\% & 87.14\% & 90.29\% \\
        Degree & 97.41\% & \textbf{87.29\%} & \textbf{90.44\%} \\
        Gender & 96.89\% & 87.10\% & 90.25\% \\
        Number & 96.71\% & 86.99\% & 90.10\% \\
        Type & 97.40\% & 87.11\% & 90.25\% \\
        Definiteness \& degree & 96.81\% & 87.23\% & 90.39\% \\
        Definiteness \& gender & 96.31\% & 87.18\% & 90.39\% \\
        Definiteness \& number & 96.78\% & 87.27\% & \textbf{90.44\%} \\
        %Degree \& gender & 96.87\% & 87.00\% & 90.16\% \\
        %Degree \& number & 96.76\% & 87.13\% & 90.26\% \\
        %Definiteness, degree \& number & 96.81\% & 87.14\% & 90.30\% \\
        \bottomrule
    \end{tabular}
    \caption{Results of experiments with modified PoS tags for adjectives.}
    \label{adjresults}
\end{table}

@@

%For a number of reasons, we do not report results from combinations of features
%for determiners, as the features could not be combined in any meaningful way.
%For instance, determiners in plural never have marked definiteness, hence this
%combination would only apply to determiners in singular and roughly correspond
%to the distinction on definiteness alone. Moreover, determiners in plural are
%not distinguished in terms of gender (thus ruling out the combination of number
%and gender), neither are definite determiners. Another aspect taken into
%consideration is that the most promising distinction, definiteness, applies to
%such a small number of tokens that more fine-grained distinctions would be
%overly sparse.

@@

Gender, on the other hand, improved the parsing, but complicated the tagging,
as the various genders are often difficult to differentiate, especially so in
the case of masculine and feminine, which share many of the same determiners.
The number of a determiner, i.e., singular or plural, led to a small increase
in tagger accuracy and LAS, while marginally lower UAS, 90.18\%, 0.01
percentage points lower than that of the original tag set. The
introduction of definiteness to the determiners led to the best parsing
results, LAS of 87.30\% and UAS of 90.42\%, while also increasing the tagger
accuracy slightly. The increase in LAS and UAS is rather interesting, as there
are only 121 determiner tokens with marked definiteness in the development
data. As this accounts for a very small number of tokens, we did not consider
further fine-grained modifications with definiteness. This goes to show that
tokens with overt definiteness have noticeable impact on the syntactic parsing,
and that distinguishing on definiteness is very beneficial.

@@

The results in Table \ref{pronresults} show that number, person and type are
the most informative features for parsing, with LAS of 87.21\%, 87.22\% and
87.19\%, respectively. However, when combining number and person, we observe a
drop by more than 0.2 percentage points, indicating that these features do not
interact in any syntactically distinctive way. The most interesting observation
is that all experiments exceed the tagging accuracy of the original tag set,
the most improved being the most fine-grained distinction, namely type, case
and number combined, obtaining a tagger accuracy of 97.52\%. This shows that
the introduction of more fine-grained distinctions for pronouns is beneficial
and aids the PoS tagger in disambiguating ambiguous words. While case alone
yields an LAS of 87.08\%, we found that the combination of type and case, which
is the most successful experiment in terms of parser performance, yields the
second highest tagging accuracy of 97.51\%. The reason for this is that
pronouns of different type and personal pronouns of different case exhibit
quite different properties and appear in different constructions. Pronouns in
nominative case (i.e., subjects) primarily occur before the main verb, while
pronouns in accusative case (i.e., objects) occur after the main verb, as
Norwegian exhibits so-called V2 word order, requiring that the finite verb of a
declarative clause appears in the second position, hence its name. The
combination of type and number comes in close to the performance of type and
case, with LAS of 87.27\% and UAS identical to that of type and case.

@@

\subsection{Optimized Tag Set}
\begin{table*}[ht]
    \centering
    \smaller[0.5]
    \begin{tabular}{@{}lllll@{}}
        \toprule
        \textbf{Category} & \textbf{Feature(s)} & \textbf{Acc} & \textbf{LAS} &
        \textbf{UAS} \\
        \midrule
        \emph{Baseline} & --- & 97.47\% & 87.01\% & 90.19\% \\
        Noun & Type, case \& definiteness & 97.05\% & 88.81\% & 91.73\% \\
        Verb & Finiteness & 97.35\% & 87.30\% & 90.43\% \\
        Adjective & Degree & 97.41\% & 87.29\% & 90.44\% \\
        Determiner & Definiteness & 97.49\% & 87.30\% & 90.42\% \\
        Pronoun & Type \& case & 97.51\% & 87.30\% & 90.41\% \\
        \bottomrule
    \end{tabular}
    \caption{Results of tagging and parsing with the most successful tag set
        modification for each category.}
    \label{respectiveresults}
\end{table*}

The most successful tag set modification for each PoS and their results are
seen in Table \ref{respectiveresults}. Nouns benefit by far the most from the
introduction of more fine-grained linguistically motivated distinctions, with
an LAS of 88.81\% and UAS of 91.73\%. We observe that the most promising tag
set modifications for verbs, adjectives, determiners and pronouns all reach LAS
of \textasciitilde 87.30\% and UAS of \textasciitilde 90.40\%. To investigate
the overall effect of these tag set modifications, we tested each of the
improvements in parser accuracy scores from baseline for statistical
significance using Dan Bikel's randomized parsing evaluation comparator
script\footnote{Available as \texttt{compare.pl} at
    \url{http://ilk.uvt.nl/conll/software.html}}, as used in the CoNLL shared
tasks. For the most successful tag set modification for each of the categories
seen in Table \ref{respectiveresults}, the difference in LAS from the original
tag set is statistically significant at significance level 0.05 (\emph{p}-value
< 0.05), as are all differences in UAS, except for verbs with finiteness
(\emph{p}-value 0.15) and pronouns with type and case (\emph{p}-value 0.06).

An overview of the tags in the optimized tag set can be seen in Table
\ref{optimizedtagset}, comprising three new tags for adjectives, two for
determiners, six for pronouns, seven for nouns and two for verbs, totaling 20
tags. Appending these to the original tag set comprising 19 tags, we reach a
total of 39 tags for NDT.

\begin{table}
    \centering
    \smaller[0.5]
    \begin{tabular}{@{}ll@{}}
        \toprule
        \textbf{Tag} & \textbf{Description} \\
        \midrule
        \texttt{adj|komp} & Comparative adjective \\
        \texttt{adj|pos} & Positive adjective \\
        \texttt{adj|sup} & Superlative adjective \\
        \texttt{det|be} & Definite determiner \\
        \texttt{det|ub} & Indefinite determiner \\
        \texttt{pron|pers} & Personal pronoun \\
        \texttt{pron|pers|akk} & Personal pronoun, accusative \\
        \texttt{pron|pers|nom} & Personal pronoun, nominative \\
        \texttt{pron|refl} & Reflexive pronoun \\
        \texttt{pron|res} & Reciprocal pronoun \\
        \texttt{pron|sp} & Interrogative pronoun \\
        \texttt{subst|appell} & Common noun \\
        \texttt{subst|appell|be} & Common noun, def. \\
        \texttt{subst|appell|be|gen} & Common noun, def., genitive \\
        \texttt{subst|appell|ub} & Common noun, indef. \\
        \texttt{subst|appell|ub|gen} & Common noun, indef., genitive \\
        \texttt{subst|prop} & Proper noun \\
        \texttt{subst|prop|gen} & Proper noun, genitive \\
        \texttt{verb|fin} & Finite verb \\
        \texttt{verb|infin} & Nonfinite verb \\
        \bottomrule
    \end{tabular}
    \caption{Overview of the optimized tag set.}
    \label{optimizedtagset}
\end{table}

\paragraph{Final Evaluation}
In Table \ref{finalresults}, we show the results of parsing with the optimized
tag set on the held-out test set, compared to the results obtained with the
original tag set. We see significant improvements from the original tag set on
both the development data and the held-out test data set. The improvement in
LAS on the development data is 1.86 percentage points, while 1.91 percentage
points on the held-out test data. These results indicate that the additional
linguistic information in the tags of our optimized tag set greatly aids
syntactic parsing and that optimizing an existing PoS tag set for a downstream
application can be useful and beneficial.

\begin{table}
    \centering
    \smaller[0.5]
    \begin{tabular}{@{}lllll@{}}
        \toprule
        \textbf{Data} & \textbf{Tag Set} & \textbf{Acc}
        & \textbf{LAS} & \textbf{UAS} \\
        \midrule
        \multirow{2}{*}{Dev}
        & Original & \textbf{97.47\%} & 87.01\% & 90.19\% \\
        %Full & 85.15\% & 93.48\% & 87.15\% & 90.39\% \\
        & Optimized & 96.85\% & \textbf{88.87\%} & \textbf{91.78\%} \\
        \midrule
        \multirow{2}{*}{Test}
        & Original & \textbf{97.30\%} & 86.64\% & 90.07\% \\
        %& Full & 84.27\% & 92.79\% & 87.03\% & 90.16\% \\
        & Optimized & 96.35\% & \textbf{88.55\%} & \textbf{91.41\%} \\
        \bottomrule
    \end{tabular}
    \caption{Results of tagging and parsing with the optimized tag set,
        compared to the initial tag sets. Trained and tested using
        automatically assigned tags from TnT.}
    \label{finalresults}
\end{table}
